---
title: "index"
author: "Jim Magdanz"
date: "October 17, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
suppressPackageStartupMessages({
  library(leaflet) # maps
  library(ggplot2)
  library(tidyr)
  library(dplyr)
  library(DT)
})
```

## Daily Escapement Data

Daily escapements: [Alaska Department of Fish and Game. 2017. Daily salmon escapement counts from the OceanAK database, Alaska, 1921-2017. Knowledge Network for Biocomplexity. doi:10.5063/F1TX3CKH](http://doi:10.5063/F1TX3CKH)


```{r}
esc <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Af119a05b-bbe7-4aea-93c6-85434dcb1c5e", method = "libcurl"), stringsAsFactors = FALSE)

head(esc)
```

```{r}
esc_med <- esc %>%
  separate(sampleDate, c("Year", "Month", "Day"), "-", remove=F) %>% 
  group_by(Year, Species) %>% 
  summarise(AnnualCount = sum(DailyCount)) %>% 
  group_by(Year,Species) %>% 
  summarize(medianEscapement = median(AnnualCount))

datatable(esc_med)
```

```{r}

ggplot(esc_med, aes(x=Species, y=medianEscapement)) +
  geom_col() +
  coord_flip()

```

```{r}
locations <- esc %>% 
  select(Location, Latitude, Longitude) %>% 
  group_by(Location, Latitude, Longitude) %>% 
  summarize(n =n()) %>% 
  drop_na()

 head(locations)

```


```{r}

leaflet(locations) %>% 
  addTiles() %>% 
  addMarkers(lng=~Longitude, lat=~Latitude, popup=~Location)


```



## Prepare Escapment Goal Data

Escapement Goals: [Andrew Munro and Eric Volk. 2017. Summary of Pacific Salmon Escapement Goals in Alaska with a Review of Escapements from 2007 to 2015. Knowledge Network for Biocomplexity. doi:10.5063/F1TQ5ZRG](http://doi:10.5063/F1TQ5ZRG)

```{r}

goals <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/knb.92014.1", method = "libcurl"), stringsAsFactors = FALSE)

head(goals)


```

```{r}

goals_BB <- goals %>%
  filter(Species=="Sockeye", Region == "Bristol Bay", Lower != "eliminated") %>%
  select(Species, Region, System, Lower, Upper, Type, Initial.Year) %>%
  mutate(Lower = as.numeric(Lower), Initial.Year = as.numeric(Initial.Year)) %>% 
  group_by(System)

goals_BB
```

## Join Tables 

```{r}

eval <- left_join(esc_BB, goals_BB, by = c("Location" = "System")) %>% 
  mutate(Lower.Goal.Exceeded = if_else(AnnualCount > Lower,TRUE,FALSE),
         Upper.Goal.Exceeded = if_else(AnnualCount > Upper,TRUE,FALSE),
         Goal.Met = if_else(AnnualCount >Lower & AnnualCount < Upper, TRUE,FALSE)) %>% 
  select(Region, Location, Year, Species.x, Lower, Upper, Type, AnnualCount, Goal.Met, Lower.Goal.Exceeded, Upper.Goal.Exceeded)
  

head(eval)

```

